%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% University/School Laboratory Report
% LaTeX Template
% Version 3.1 (25/3/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Linux and Unix Users Group at Virginia Tech Wiki 
% (https://vtluug.org/wiki/Example_LaTeX_chem_lab_report)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{article}

\usepackage[version=3]{mhchem} % Package for chemical equation typesetting
\usepackage{siunitx} % Provides the \SI{}{} and \si{} command for typesetting SI units
\usepackage{graphicx} % Required for the inclusion of images
\usepackage{natbib} % Required to change bibliography style to APA
\usepackage{amsmath} % Required for some math elements 

\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,      
	urlcolor=cyan,
}


%\usepackage{times} % Uncomment to use the Times New Roman font

%----------------------------------------------------------------------------------------
%	DOCUMENT INFORMATION
%----------------------------------------------------------------------------------------

\title{Assignment 1\\Professional Communication} % Title

\author{Pranav Gade}

\date{\today} % Date for the report

\begin{document}

\maketitle % Insert the title, author and date
\begin{center}
	\begin{tabular}{l r}
		Batch: & CS\&AI \\
		Roll no.: & LCI2020010
	\end{tabular}
\end{center}

\section*{Topic}

Some film companies spend millions of dollars on the production of a single movie. Is it necessary to spend a lot of money to make a good movie? What factors contribute to the success of a movie?

\section*{Essay}

Movies are entertainment for millions, with billions spent on making them every year. But, is this spending justified? In this essay, I would like to explore what could be an ideal-case scenario, and why that isn't the case. \par
I think a great movie comes from a creative story. For example, the movie 'Dave Made a Maze' was created from start to finish in a single apartment, and it is one of the best and most creative movies I have seen. However, this appears to be the exception, not the norm. In an ideal case, spending millions on just a couple of minutes of special effects would sound ludicrous to anyone. However, this has been the norm in most modern movies. \par
Let us take a look at the justification of this cost from a game theory perspective. First, writing good stories is hard. So if an author is offered money, they will very likely grant a license to whoever will make them most money. For example, J.K. Rowling made \$650 million from the Harry Potter series. So, if she was promised, say, \$10,000 by another director, she would obviously take \$650 million. I believe that this is where the 'spending' starts. No one would pay \$650 million for the story, and spend just \$1 million on the production. After this, people are more likely to watch their favorite movie star, because that is another guarantee that the movie would be great. Finally, you might as well get the best film equipment and special effects. All this brings our Harry Potter series at an impressive \$1.2 billion! The producers, however, will keep pouring the money in, because that \$1.2 billion generated an impressive \$7.7 billion, which made \$1.2 billion a really good investment. So, as long as movies make billions, there will be someone pouring billions in them. \par
Therefore, I would conclude by saying that although spending billions on movies isn't justified, it has become a necessity for a good movie, in part due to the amount good movies make in box office, and in part due to the rarity of good stories and authors.


\end{document}
